On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2020-08-04 manuscripts/IEEE/submission/referee_responses.txt

-------------------------------------
Response: We are curious as well, and this observation is a main motivation for our work. Imagining that natural image patches form a population which satisfies (1) with respect to some ground truth dictionary A, we have shown that there exists a sufficient number of samples to uniquely identify it or something close to it via approximate solutions. Given this fundamental stability and uniqueness of the problem solutions, the fact that a variety of methods geared to approximately solve Problems 1 and 2 all seem to capture similar structure is much less surprising.
-------------------------------------

REVIEWER 2

Comments
This paper studies the conditions under which the dictionary learning problem is well-posed, under the assumption of additive noise. Overall I think it is nicely written.
I have some doubts about (1) efficiency of checking the assumption stated in theorem 1; (2) numerically solving the optimization problem as stated in eqn (4) in practice. I personally think rephrasing some of the graph theoretic terms will make the paper easier to follow, but that might just be personal preference.

-------------------------------------
Response: Thanks for your comments. (1) Although computable, indeed, checking the conditions of assumptions in our theorems is often NP-hard as we explain in the manuscript; we have updated the revision for more clarity on this. (2) We also believe that this numerical optimization is NP-hard and include this question in the revised discussion; further, we now pose the problem of whether the more tractable l1 norm version implies the same uniqueness results.
-------------------------------------
